---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# FPLConnect

<!-- badges: start -->
<!-- badges: end -->

The goal of FPLConnect is to make it easyer to connect to EDP database or the Gulf Data Warehouse in AWS when using RStudio. 

## Installation

```{r installation}
# You can install the development version of FPLConnect like so:
devtools::install_github("ham1hv9/FPLConnect")

```

## Usage
A fairly common task when trying to connect to either the FPL's EDP database or the Gulf Data Warehouse.

``` r
# Required Packages (devtools, DBI & odbc).
```

## Example

This is a basic example which shows you how to connect to either the Gulf Data Warehouse or EDP on AWS:

```{r example}
library(FPLConnect)
## basic example code

# To Connect to EDP
con <- connect_to_EDP(user, password)

# To Connect to the Gulf Data Warehouse
con1 <- connect_to_GULF_DW(user, password)
```

